---
title: "R Notebook"
output: html_notebook
---

```{r}
student <- read.csv("C:/Users/Alfa/Desktop/Statistik/student.csv")
View(student)
```


## Explanation of Columns

Pstatus
Parent's cohabitation status (binary: 'T' - living together or 'A' - living apart)

famsize
Family size (binary: 'LE3' - less or equal to 3 or 'GT3' - greater than 3)

Medu
Mother's education (numeric: 0 - none, 1 - primary education (4th grade), 2 - 5th to 9th grade, 3 - secondary education, or 4 - higher education)

Fedu
Father's education (numeric: 0 - none, 1 - primary education (4th grade), 2 - 5th to 9th grade, 3 - secondary education, or 4 - higher education)

Mjob
Mother's job (nominal: 'teacher', 'health' care related, civil 'services' (e.g. administrative or police), 'at_home' or 'other')

Fjob
Father's job (nominal: 'teacher', 'health' care related, civil 'services' (e.g. administrative or police), 'at_home' or 'other')

G1
First period grade (numeric: from 0 to 20)

G2
Second period grade (numeric: from 0 to 20)

G3
Final grade (numeric: from 0 to 20, output target)




```{r}
hist(student$G1, xlab = "First Semester Noten", ylab= "Anzahl", main ="Histogramm der First Semester Noten", breaks = 7,  col = "skyblue")

```


```{r}
hist(student$G2, xlab = "Second Semester Noten", ylab= "Anzahl", main ="Histogramm der First Semester Noten", breaks = 7,  col = "skyblue")

```

```{r}
hist(student$G3, xlab = "Final Semester Noten", ylab= "Anzahl", main ="Histogramm der First Semester Noten", breaks = 7,  col = "skyblue")

```



```{r}
hist(student$age, xlab = "Age", ylab= "Anzahl", main ="Histogramm of A", breaks = 7,  col = "skyblue")

```

```{r}
hist(student$Medu, xlab = "Education of Mother", ylab= "Anzahl", main ="Histogramm of Mother Education", breaks = 7,  col = "skyblue")

```

```{r}
hist(student$Fedu, xlab = "Education of Father", ylab= "Anzahl", main ="Histogramm of Father Education", breaks = 6,  col = "skyblue")

```
```{r}
hist(student$freetime, xlab = "Freetime", ylab= "Anzahl", main ="Histogramm of Freetime", breaks = 5,  col = "skyblue")

```
```{r}
hist(student$studytime, xlab = "Study Time", ylab= "Anzahl", main ="Histogramm of Studytimes", breaks = 4     ,  col = "skyblue")

```


```{r}
plot(student$G3 ~ student$studytime, main = "Streudiagramm zwischen Final Grade and Studytime", xlab = "Final Grade", ylab= "")
abline(lm(student$G3 ~ student$studytime, data =student), col="tomato")

```

```{r}
test <- cor.test(student$G3, student$studytime)
test
```


```{r}
plot(student$G1 ~ student$G3, main = "Streudiagramm zwischen Final Grade and Studytime", xlab = "First Grade vs Final Grade", ylab= "")
abline(lm(student$G1 ~ student$G3, data =student), col="tomato")

```

```{r}
test1 <- cor.test(student$G3, student$G1)
test1



```



```{r}
test2 <- cor.test(student$G3, student$Fedu)
test2
```
```{r}
test3 <- cor.test(student$G3, student$Medu)
test3
```


```{r}
test4 <- cor.test(student$Fedu, student$Medu)
test4
```

```{r}
plot(student$G3 ~ student$studytime, main = "", xlab = "Study Time", ylab= "Final Grade")
abline(lm(student$G3 ~ student$studytime, data = student), col="tomato")
```

```{r}
plot(student$G3 ~ student$Medu, main = "", xlab = "First Grade", ylab= "Final Grade")
abline(lm(student$G3 ~ student$G1, data = student), col="tomato")
```


```{r}
plot(student$G3 ~ student$Fedu, main = "", xlab = "Father Education", ylab= "Final Grade")
abline(lm(student$G3 ~ student$Fedu, data = student), col="tomato")
```


# T Test für unabhängige Stichproben


## 4) Deskriptive Statistiken

```{r}
library(dplyr)
student %>%
group_by(internet) %>%
  summarize(Anzahl = n(), Mittelwert = mean(G3), Median = median(G3), Standardabweichung = sd(G3)) %>%
  mutate_if(is.numeric, round, 2)
```

### Internet

```{r}
library(car)

leveneTest(student$G3, student$internet, center = mean)
```

Mit Welch-Korrektur: p < 0.05 => Ergebnis Signifikant –> Varianzen heterogen

Ohne Welch-Korrektur: p > 0.05 => Ergebnis nicht Signifikant –> Varianzen homogen –> H0 mit Annahme Var1=Var2

## 6) Ergebnisse des t-Tests für unabhängige Stichproben (Variant 1:Ohne Welch-Korrektur)

```{r}
##ungerichtete Hypothese
test1<- t.test(student$G3~student$internet, var.eq = TRUE, con= 0.95, alt = "two.sided")
test1
```

### Activities

```{r}
library(car)

leveneTest(student$G3, student$activities, center = mean)
```

Mit Welch-Korrektur: p < 0.05 => Ergebnis Signifikant –> Varianzen heterogen

Ohne Welch-Korrektur: p > 0.05 => Ergebnis nicht Signifikant –> Varianzen homogen –> H0 mit Annahme Var1=Var2

## 6) Ergebnisse des t-Tests für unabhängige Stichproben (Variant 1:Ohne Welch-Korrektur)

```{r}
##ungerichtete Hypothese
test1<- t.test(student$G3~student$activities, var.eq = TRUE, con= 0.95, alt = "two.sided")
test1
```

### Guardian

```{r}
library(car)

leveneTest(student$G3, student$guardian, center = mean)
```

Mit Welch-Korrektur: p < 0.05 => Ergebnis Signifikant –> Varianzen heterogen

Ohne Welch-Korrektur: p > 0.05 => Ergebnis nicht Signifikant –> Varianzen homogen –> H0 mit Annahme Var1=Var2

## 6) Ergebnisse des t-Tests für unabhängige Stichproben (Variant 1:Ohne Welch-Korrektur)

```{r}
##ungerichtete Hypothese
test1<- t.test(student$G3~student$guardian, var.eq = TRUE, con= 0.95, alt = "two.sided")
test1
```
We can't do this test. 

### Paid

```{r}
library(car)

leveneTest(student$G3, student$paid, center = mean)
```

Mit Welch-Korrektur: p < 0.05 => Ergebnis Signifikant –> Varianzen heterogen

Ohne Welch-Korrektur: p > 0.05 => Ergebnis nicht Signifikant –> Varianzen homogen –> H0 mit Annahme Var1=Var2




## 6) Ergebnisse des t-Tests für unabhängige Stichproben (Variant 1:Ohne Welch-Korrektur)

```{r}
##ungerichtete Hypothese
test1<- t.test(student$G3~student$paid, var.eq = TRUE, con= 0.95, alt = "two.sided")
test1
```

## 6) (Variant 2:Welch-Korrektur)

```{r}
##ungerichtete Hypothese
test1<- t.test(student$G3~student$paid, var.eq = FALSE, con= 0.95, alt = "two.sided")
test1
```

### GENDER

```{r}
library(car)

leveneTest(student$G3, student$sex, center = mean)
```

Mit Welch-Korrektur: p < 0.05 => Ergebnis Signifikant –> Varianzen heterogen

Ohne Welch-Korrektur: p > 0.05 => Ergebnis nicht Signifikant –> Varianzen homogen –> H0 mit Annahme Var1=Var2

## 6) Ergebnisse des t-Tests für unabhängige Stichproben (Variant 1:Ohne Welch-Korrektur)

```{r}
##ungerichtete Hypothese
test1<- t.test(student$G3~student$sex, var.eq = TRUE, con= 0.95, alt = "two.sided")
test1
```
### (Variant 2:Welch-Korrektur)

```{r}
##ungerichtete Hypothese
test1<- t.test(student$G3~student$sex, var.eq = FALSE, con= 0.95, alt = "two.sided")
test1
```
# T Test für abhängige Stichproben

# Differenz erstellen

```{r}
zwischen <- student$G1 - student$G2 
zwischen
```
```{r}
zwischen1 <- student$G1 - student$G3 
zwischen1
```

```{r}
hist(zwischen, xlab = "First Semester Noten", ylab= "Anzahl", main ="Histogramm der First Semester Noten", breaks = 7,  col = "skyblue")

```
```{r}
hist(zwischen1, xlab = "First Semester Noten", ylab= "Anzahl", main ="Histogramm der First Semester Noten", breaks = 7,  col = "skyblue")

```
# Die Spalte "Differenz" wird zum Datensatz hinzugefügt

```{r}
# Die Spalte "Differenz" wird zum Datensatz hinzugefügt
student1 <- cbind(student, "Differenz" = zwischen)
View(student1)
```


```{r}
hist(student1$Differenz, xlab = "Differenz zwischen First Grade and Second Grade", ylab= "Anzahl", main ="Histogramm der Differenz", breaks =6,  col = "skyblue")
```

```{r}
library(car)
```


```{r}
qqPlot(student1$Differenz, main = "QQPlot für die Var. Differenz")
```

#### We can do other part of the test with outliers and by removing outliers.


```{r}

boxplot(student1$Differenz) # Boxplot
# Suche der Ausreiser
outliers <- boxplot(student1$Differenz, plot=FALSE)$out 
#Ausgabe der Ausreiser
print(outliers)
#Wegfilter der Ausreiser
student_wo <- student1[-which(student1$Differenz %in% outliers),]
#Boxplot
boxplot(student_wo$Differenz)

```
```{r}
testVER<- t.test(student_wo$G1, student_wo$G2, alternative = "two.sided", paired = TRUE, conf.level = .95)

testVER
```

```{r}
testVER<- t.test(student_wo$G1, student_wo$G3, alternative = "two.sided", paired = TRUE, conf.level = .95)

testVER
```
```{r}
eff1 <- sqrt(testVER$statistic^2 / (testVER$statistic^2 + testVER$parameter))

sprintf("Effektstärke: %.4f",eff1)
```

## 4)	Boxplots 

```{r}
boxplot(student1$G3 ~student1$Mjob, main = "Boxplots zum Vergleich", ylab = "Final Grade", xlab= "Job of Mother" , col = c("lightgreen", "deepskyblue","tomato", "orange"))
```
```{r}
boxplot(student1$G3 ~student1$Fjob, main = "Boxplots zum Vergleich", ylab = "Final Grade", xlab= "Job of Father" , col = c("lightgreen", "deepskyblue","tomato", "orange"))
```
```{r}
boxplot(student1$G3 ~student1$guardian, main = "Boxplots zum Vergleich", ylab = "Final Grade", xlab= "Guardian" , col = c("lightgreen", "deepskyblue","tomato"))
```

```{r}
boxplot(student1$G3 ~student1$reason, main = "Boxplots zum Vergleich", ylab = "Final Grade", xlab= "Reason" , col = c("lightgreen", "deepskyblue","tomato", "orange"))
```

```{r}
boxplot(student1$G3 ~student1$Dalc, main = "Boxplots zum Vergleich", ylab = "Final Grade", xlab= "Reason" , col = c("lightgreen", "deepskyblue","tomato", "orange"))
```
```{r}
boxplot(student1$G3 ~student1$Walc, main = "Boxplots zum Vergleich", ylab = "Final Grade", xlab= "Reason" , col = c("lightgreen", "deepskyblue","tomato", "orange"))
```

```{r}
boxplot(student1$G3 ~student1$famsup, main = "Boxplots zum Vergleich", ylab = "Final Grade", xlab= "Family " , col = c("lightgreen", "deepskyblue"))
```
```{r}
boxplot(student1$G3 ~student1$schoolsup, main = "Boxplots zum Vergleich", ylab = "Final Grade", xlab= "Family " , col = c("lightgreen", "deepskyblue"))
```

```{r}
boxplot(student1$G3 ~student1$studytime, main = "Boxplots zum Vergleich", ylab = "Final Grade", xlab= "Family " , col = c("lightgreen", "deepskyblue"))
```


```{r}
boxplot(student1$G3 ~student1$traveltime, main = "Boxplots zum Vergleich", ylab = "Final Grade", xlab= "Family " , col = c("lightgreen", "deepskyblue"))
```

```{r}
boxplot(student1$G3 ~student1$famsize, main = "Boxplots zum Vergleich", ylab = "Final Grade", xlab= "Family " , col = c("lightgreen", "deepskyblue"))
```





```{r}
boxplot(student1$G3 ~student1$Medu, main = "Boxplots zum Vergleich", ylab = "Final Grade", xlab= "Family " , col = c("lightgreen", "deepskyblue"))
```


```{r}
boxplot(student1$G3 ~student1$Fedu, main = "Boxplots zum Vergleich", ylab = "Final Grade", xlab= "Family " , col = c("lightgreen", "deepskyblue"))
```

## Mehranova


## Boxplot

```{r}
ggplot(student1, aes(sex, G3, fill=factor(Mjob))) +
geom_boxplot() +
theme_minimal()+
labs(fill = "Job of Mother", x="Geschlecht", y="Final Grades")
```

```{r}
ggplot(student1, aes(sex, G3, fill=factor(Medu))) +
geom_boxplot() +
theme_minimal()+
labs(fill = "Job of Mother", x="Geschlecht", y="Final Grades")
```
```{r}
ggplot(student1, aes(sex, G3, fill=factor(Fedu))) +
geom_boxplot() +
theme_minimal()+
labs(fill = "Job of Mother", x="Geschlecht", y="Final Grades")
```



```{r}
ggplot(student1, aes(sex, G3, fill=factor(guardian))) +
geom_boxplot() +
theme_minimal()+
labs(fill = "Job of Mother", x="Geschlecht", y="Final Grades")
```